\sysfull

### 2017-08-11 paper/evaluation.tex
added WISP info for CMU
fix typo

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used internal timer for measuring run time. For harvested energy, we used the ThingMagic Astra-EX integrated RFID reader set at 30\,dBm transmission power. We used EDB~\cite{edb} to measure run time. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0 was used for both Clang and LLVM.

@@

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging macro ({\tt RVAR} and {\tt WVAR}) in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

>>>>

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used internal timer for measuring run time. For harvested energy, we used WISP\,5.0~\cite{wisp5,wisp} hardware and ThingMagic Astra-EX integrated RFID reader set at 30\,dBm transmission power. We used EDB~\cite{edb} to measure run time. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0 was used for both Clang and LLVM.

@@

We start with evaluating the efficiency of the \sys compiler. Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging macro ({\tt RVAR} and {\tt WVAR}) in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.
